\documentclass{resume}

\usepackage[left=0.5 in,top=0.5in,right=0.5 in,bottom=0.5in]{geometry}
\usepackage{hyperref}
\usepackage{fontawesome5}

\begin{document}
\vspace*{-1.5cm}


\begin{center}
    {\LARGE \textbf{MOHD RAHIL KHAN}} \\[6pt]
    \faEnvelope\ \href{mailto:khanmohdrahil44@gmail.com}{khanmohdrahil44@gmail.com} \quad
    \faPhone\ +91 7987105532 \\[4pt]
    \faLinkedin\ \href{https://www.linkedin.com/in/mohdrahilkhan14}{/mohdrahilkhan14} \quad
    \faGithub\ \href{https://github.com/supineboi}{/supineboi}
\end{center}

\vspace{8pt}

%----------------------------------------------------------------------------------------
\begin{rSection}{PROFESSIONAL SUMMARY}

Full Stack Engineer with 3+ years of experience architecting scalable SaaS systems and high-volume data workflows. Delivered production-grade third-party integrations across major marketing platforms and led seamless database migrations at scale. Strong focus on modular architecture, performance optimization, and secure authentication design.

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming & JavaScript (ES6+), Python, PHP \\
Frontend & React.js, Next.js, Redux Toolkit, Ant Design, HTML5, CSS3, Tailwind CSS \\
Backend & Node.js, Django, Drupal \\
Databases \& Caching & DynamoDB, MongoDB, PostgreSQL, MySQL, MS SQL, Redis, Elasticsearch \\
Cloud \& APIs & AWS (EC2, ECS, S3, DynamoDB, Lambda, SNS, CloudWatch), REST APIs, MFA \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{WORK EXPERIENCE}

\textbf{Associate Software Developer, Fragmatic} \hfill \textbf{Delhi | Oct 2023 – Present}

\begin{itemize}
\item Architected and scaled core backend systems by building a distributed batch processing pipeline to evaluate millions of profiles for segmentation. Led end-to-end migration from MongoDB (Mongoose) to DynamoDB (Dynamoose), introducing reusable utilities, custom ORM extensions, Redis caching, and multi-tenant scope isolation.
\item Led full-cycle third-party integrations across Meta, Google, LinkedIn, HubSpot, Klaviyo, Mailchimp, Webflow, and Constant Contact, implementing OAuth 2.0 token lifecycle handling, campaign data ingestion pipelines, and securing marketplace approvals.
\item Engineered a modular plugin architecture separating integrations and utilities, refactored legacy Redux to Redux Toolkit, and implemented secure token-based authentication in Next.js with 2FA and centralized email templating.
\item Delivered platform tooling including admin dashboard (organization management, AWS cost monitoring, integration configs), large-scale profile generators for stress testing, Redis-backed caching strategies, and a multi-agent chatbot using Agno framework.
\end{itemize}

\vspace{0.3cm}

\textbf{Associate Software Developer, OpenSense Labs} \hfill \textbf{Bhopal | Jul 2023 - Oct 2023}

\begin{itemize}
\item Built and customized Drupal websites using theming and custom modules to deliver responsive, accessible platforms.
\item Developed background queue jobs for reliable large-scale CSV exports with scheduled and streamed processing.
\end{itemize}

\vspace{0.3cm}

\textbf{Full Stack Engineer (Freelance)} \hfill \textbf{Bhopal | Oct 2022 – Jul 2023}

\begin{itemize}
\item Built and deployed a Django-based e-commerce platform for Green Diary Farm using MS SQL and secure PhonePe payment integration.
\item Delivered an admin dashboard for invoicing, order tracking, inventory management, and reporting.
\end{itemize}

\end{rSection}


%----------------------------------------------------------------------------------------
\begin{rSection}{EDUCATION}

\textbf{B.Tech – Electronics and Communication Engineering} \hfill Jul 2019 – Jul 2023 \\
University Institute of Technology, RGPV, Bhopal

\end{rSection}

\end{document}
